Toxic Code Snippets on Stack Overflow

### 2018-11-28 cloverflow-tse/cloverflow.tex
Shortened Matheus' bio.

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is currently a Research Assistant in the Computer Science Department at State University of Ceara. He recently received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He was supervised by Prof. Mark Harman and Dr. Jens Krinke. His research interests include software architecture, search-based software engineering, mining software repositories, modern code review and empirical software engineering.
\end{IEEEbiography}
%\vspace{-1cm}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
is Research Assistant in the Computer Science Department at State University of Ceara. He received his PhD degree at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. His research interests include software architecture, search-based software engineering, mining software repositories, and modern code review.
\end{IEEEbiography}
%\vspace{-1cm}
